Twists of supersymmetric gauge theories

### 2019-07-16 10d_section_draft.tex
Sketching in the content in the 10d argument

\section{Twists}
\subsection{Dimension 10}

>>>>

\section{Twists}
\subsection{Dimension 10}
\chris{background, recall there is only one class of twists, by a pure spinor.  There's a trivial twisting homomorphism from $\SU(5)$, and so it's defined on CY5s.  Give names to the BV component fields as irreducible $\SU(5)$ representations: this is important for the argument below.}

\begin{theorem}
The holomorphic twist of 10d super Yang-Mills theory on a Calabi-Yau 5-fold $X$ is equivalent to holomorphic Chern-Simons theory on $X$.
\end{theorem}

\begin{proof}
\chris{recall the steps.  1) Modify $\chi^\vee$ by a linear change of variables $\chi^\vee \mapsto \chi^vee + \Lambda F_{1,1}$. 2) Integrate out the contractible doublet $\chi, \chi^\vee$.  3) Note that the pairs $A_{1,0}, \psi$ and $\psi^\vee, A_{1,0}^\vee$ can be killed in pairs, and the composite of these operations defines a symplectomorphism.  4) These steps each preserve the action, so that we have a map of interacting theories. 5) Using the spectral sequence, this map is an equivalence.}
\end{proof}
